Title of the Master Thesis

### 2015-10-01 Master Thesis/synopsis.tex
Starting section "Local correspondence"

>>>>

\begin{lemma}
Let $K$ be henselian with respect to $w\in|\operatorname{Spv}(K)|$. Set $k=k(w)$ and $\Gamma = \Gamma_w$. Then $k$ is an algebraic extension of a finite field $\mathbb{F}_p$. Let $\ell\neq p$ be a prime and assume $\mu_\ell\subset K$. Then the following conditions are equivalent:
\begin{enumerate}[(i)]
\item $\mathrm{H}^3(K,\mathbb{Z}/\ell\mathbb{Z})=\mathbb{Z}/\ell\mathbb{Z}$
\item $\ell^\infty\nmid[k:\mathbb{F}_p]$ and $\dim_{\mathbb{F}_\ell}(\Gamma/\ell\Gamma) = 2$
\end{enumerate}
Otherwise we have $\mathrm{H}^3(K,\mathbb{Z}/\ell\mathbb{Z})=0$. If $L/K$ is an algebraic extension and (i) holds, we have:
\[ \mathrm{H}^3(L,\mathbb{Z}/\ell\mathbb{Z}) = \begin{cases}
\mathbb{Z}/\ell\mathbb{Z}, & \ell^\infty\nmid [L:K]\\
0, & \text{otherwise}
\end{cases} \]
\end{lemma}

\begin{proposition}
Let $K_0/K$ be an algebraic extension.
\begin{enumerate}[(i)]
\item Suppose there exists a prime number $\ell$ with $\ell^\infty\nmid[K_0:K]$ and such that for every algebraic extension $L/K_0$ we have: 
\[ \mathrm{H}^3(L,\mathbb{Z}/\ell\mathbb{Z}) = \begin{cases}
\mathbb{Z}/\ell\mathbb{Z}, & \ell^\infty\nmid [L:K_0]\\
0, & \text{otherwise}
\end{cases} \]
Then there exists a unique henselian $w\in|\operatorname{Spv}(K)|$.
\item Assume that the hypothesis of (i) is satisfied for two different prime numbers. Then $w$ is defectless.
\end{enumerate}
\end{proposition}

\section{Local correspondence}

Let $K,K'$ be two finitely generated fields of characteristic $0$ and dimension $2$ and $\sigma:G_K\to G_{K'}$ be an isomorphism of profinite groups. For intermediate fields $L$ of $\overline{K}/K$ the corresponding intermediate field of $\overline{K'}/K'$ will be denoted by $L'$. In other words $\sigma G_L=G_{L'}$.

\begin{lemma}
Let $w\in\operatorname{Spv}_\text{d}^{(2)}(K)$ and let $E=K_w$ be a henselization of $w$. Then $E'$ is a henselization of $K'$ with respect to a unique $w'\in\operatorname{Spv}_\text{d}^{(2)}(K')$. The map $w\mapsto w'$ does not depend on the choice of the henselization.
\end{lemma}

\begin{lemma}
$\sigma$ induces a bijection $\sigma:\operatorname{Spv}_\text{d}^{(1)}(K)\to\operatorname{Spv}_\text{d}^{(1)}(K')$. If $E=K_v\subset\overline{K}$ is a henselization of $K$ with respect to $v\in\operatorname{Spv}_\text{d}^{(1)}(K)$ then $E'$ is a henselization of $K'$ with respect to $v'=\sigma(v)$.
\end{lemma}
